Red-Giant Hot Jupiters: Brilliant Radio Emitter?

### 2015-04-13 ms.tex

Not only luminous, red giants lose their masses at high rate, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991} for RGs \memo{How these values are observationally obtained?}. \memo{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memo{cite more papers?}. 
Jovian planets in orbit around such
stars can be transiently heated to hot-Jupiter temperatures
($\sim$1000~K or more) at distances out to tens of AU, depending on
the star's mass. These planets' existence was predicted by
\citet{spiegel+madhusudhan2012} and we will refer to them as
``red-giant hot Jupiters'' (RGHJs). 
When massive stellar wind reach the planetary magnetosphere standoff points  \memo{??}, they presumably deposit part of their energy generating bright radio emission.

@@

The mass loss rate of the stellar wind can be estimated from observation \memo{How?}. For the known red giants, the values are typically $\dot M \sim 10^{-8} M_{\odot}$/yr, and can be as much as $\sim  10^{-5} M_{\odot }$/yr for AGB stars, significantly greater than the solar mass-loss rate: $\sim 10^{-14} M_{\odot}$/yr. 
\begin{equation}
\frac{\dot M}{\dot M_{\odot}} \sim 10^6
\end{equation}

@@

Theoretically, the magnetic moment of gaseous planets are expressed with the following scaling relationship \citep{griebmeier2004}:
%%%%%%%%%% 
\begin{equation}
\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
\end{equation}
%%%%%%%%%%
where $\omega $ is the spin angular velocity, $\rho _c$, $r_c$ and $\sigma $ are the density, the radius, and the conductivity of the ``dynamo region'' where the density is high enough for hydrogen to be metallic, respectively. 
The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}. \memo{validity?}

@@

We assume that the conductivity $\sigma $ is the same as Jupiter \memo{?}.

@@

\memo{Following arguments are based on \citep{griebmeier2007}. }
Assuming $P_{\rm inp, J} = 2.1\times 10^{11}$ W \citep{griebmeier2007}, observed RGHJ radio emission at distance $l$ is
\begin{eqnarray}
P_{\rm obs} &=& \frac{P_{\rm radio}}{\Omega l^2 f_{\rm cyclotron}} \\
&\approx & 5\times 10^{-6} \mbox{Jy} \left( \frac{P_{\rm radio}}{P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{[pc]}} \right)^{-2} \left( \frac{B}{10\mbox{[G]}} \right) ^{-1} \\
&\approx & 10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{[pc]}} \right)^{-2} \left( \frac{B}{10\mbox{[G]}} \right) ^{-1}
\end{eqnarray}
where $\Omega $ is the solid angle of emission, which is assumed $\Omega = 1.6$.

>>>>

Not only luminous, red giants lose their masses at high rate, typically $\sim  10^{-8} M_{\odot }$/yr \citep{judge1991} \memoYF{How these values are observationally obtained?} \memoYF{Dave mentioned $\sim  10^{-5} M_{\odot }$/yr, where does this come from?} through massive (but slow) stellar wind \citep{suzuki2008} \memoYF{cite more papers?}.

Jovian planets in orbit around such
stars can be transiently heated to hot-Jupiter temperatures
($\sim$1000~K or more) at distances out to tens of AU, depending on
the star's mass. These planets' existence was predicted by
\citet{spiegel+madhusudhan2012} and we will refer to them as
``red-giant hot Jupiters'' (RGHJs). 
When massive stellar wind reach the planetary magnetosphere standoff points  \memoYF{??}, they presumably deposit part of their energy generating bright radio emission.

@@

The mass loss rate of the stellar wind can be estimated from observation \memoYF{How?}.
For the known red giants, the values are typically $\dot M \sim 10^{-8} M_{\odot}$/yr, and can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases, significantly greater than the solar mass-loss rate $\sim 10^{-14} M_{\odot}$/yr.

%\memoDS{Can be as high as $10^{-5} M_\odot~{\rm yr^{-1}}$ during AGB phases.  I'm calling it ``red giant'' but we're really thinking of AGB stars for maximum mass-loss and brightness.}
%>>>>>>> e6e562d36dff6e5bb10b57fdd066ee5edd32b496
\begin{equation}
\frac{\dot M}{\dot M_{\odot}} \sim 10^6
\end{equation}

@@

Theoretically, the magnetic moment of gaseous planets are expressed with the following scaling relationship \citep{griebmeier2004}:
%%%%%%%%%% 
\begin{equation}
\mathcal{M} \propto  \omega ^{\alpha } \rho_c ^{\beta } r_c^{\gamma } \sigma ^{\delta }
\end{equation}
%%%%%%%%%%
where $\omega $ is the spin angular velocity, $\rho _c$, $r_c$ and $\sigma $ are the density, the radius, and the conductivity of the ``dynamo region'' where the density is high enough for hydrogen to be metallic, respectively. 
The scaling indexes are estimated to be $\alpha \sim 1/2-1$, $\beta \sim 1/2$, $\gamma \sim 3-4$, and $\sigma \sim -1/2-0$. In this paper, we assume $\alpha =1$, $\beta =1/2$, and $r_c = 7/2$ \citep{sano1993}. \memoYF{validity?}

@@

We assume that the conductivity $\sigma $ is the same as Jupiter \memoYF{?}.

@@

\memoYF{Following arguments are based on \citep{griebmeier2007}. }
Assuming $P_{\rm inp, J} = 2.1\times 10^{11}$ W \citep{griebmeier2007}, observed RGHJ radio emission at distance $l$ is
\begin{eqnarray}
P_{\rm obs} &=& \frac{P_{\rm radio}}{\Omega l^2 f_{\rm cyclotron}} \\
&\approx & 5\times 10^{-6} \mbox{Jy} \left( \frac{P_{\rm radio}}{P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{[pc]}} \right)^{-2} \left( \frac{B}{10\mbox{[G]}} \right) ^{-1} \\
&\approx & 10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{[pc]}} \right)^{-2} \left( \frac{B}{10\mbox{[G]}} \right) ^{-1}
\end{eqnarray}
where $\Omega $ is the solid angle of emission, which is assumed $\Omega = 1.6$.
